---
title: "Soccer Analytics"
author: "Kapil Khanal"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## - Data Analysis of events vs Data Analysis of entities
 - How are event data collected? 
 - How to work with event data in R


### - Basics of R
 - R is not like Java or C++ or Python. But programming skills transfers 
 - It makes it easier to work with Data. 
 
The primary data structure in R is a vector
A vector is like an array/list in other programming language

R is a functional langauge which means you work with functions not objects and methods. 

Focus on data and functions to manipulate them 

Data is usually in table format also called as dataframe
Many data manipulation function also called as verbs are used 

Analyzing your data and Plotting your data follows a grammatical format

#### Example of data wrangling grammer
First select the columns, then mutate or change or filter on them and then add some more relevant data and plot it

R workflow consists of %>% also called as pipe. Data is like water which follows through data manipulation functions. At the end you collect data 

top_n <-data %>% select() %>% mutate() %>% filter() %>% mutate() %>% select() %>% arrange() %>% count() %>% top_n()


Main Data Structure is "data.frame"

data.frame is basically a table with rows and columns. We mostly refer to columns..add columns, change columns..that is called column oriented workflow. One can do row oriented as well but is not common

Above data is flowing through the functions

```{r}
library(tidyverse)
```


```{r}
barca_real_data<-read.csv("https://raw.githubusercontent.com/KapilKhanal/Sports_Analytics_workshop/master/barca_vs_real.csv")
```
#### Example of Data following through code(functions)
```{r}
View(head(barca_real_data))
```



```{r}
top_duration_by_possesion<-barca_real_data %>% group_by(possession,team.name) %>% 
        summarise(maximum_possesion  = max(duration)) %>% 
        top_n(10) %>%
        arrange(desc(maximum_possesion))
View(top_duration_by_possesion)
```


```{r}
ggplot(data= top_duration_by_possesion,aes(y= maximum_possesion,x = team.name ,color = team.name)) +
        geom_violin() + 
        geom_jitter() + 
        stat_boxplot(geom="errorbar", width=.5)+
        theme_linedraw() 
```
```{r}
top_duration_by_possesion %>% 
        group_by(team.name) %>% 
        summarise(mean_duration = mean(maximum_possesion)) 


```
Are they really significantly different?
Nope.As conformed from the test below..
```{r}

t.test(maximum_possesion~team.name,data = top_duration_by_possesion)
```

